---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

# Load the package
library(tidyverse)
```

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQrNunzhP5CZfWI6cKoZlIcAcCDivqJsC3pkOkbH42sezDUYQzhS3dNAW-SdcBfsntPn8ejqgFdjCk5/pub?output=csv")

# 1. Rename the variables
latest_data <- logged_data %>%
  rename(
    timestamp = 1,
    platform = 2,
    duration_sec = 4,
    ad_content = 6
  ) %>%
  # Drop all other columns
  select(timestamp, platform, duration_sec, ad_content)

# 2. Summary Statistics
total_ads <- latest_data %>% 
  nrow()

avg_duration <- latest_data$duration_sec %>% 
  mean(na.rm = TRUE) %>% 
  round(1)

longest_ad <- latest_data$duration_sec %>% 
  max(na.rm = TRUE)
```


```{css}
body {
  font-family: Arial, sans-serif;
  line-height: 1.6;
  color: black;
}

h2 {
  color: black;
  border-bottom: 2px solid blue;
  padding-bottom: 5px;
}

.summary-text {
  background-color: white;
  padding: 15px;
  border-left: 4px solid blue;
  border-radius: 4px;
  margin-bottom: 20px;
}
```

## Analysis of Targeted Ads

This dynamic report tracks and visualises targeted advertisements observed across different digital platforms over a recent period. It specifically focuses on identifying the distribution of these ads by platform and understanding their varying durations.

<div class="summary-text">
Based on a total of <strong>`r total_ads`</strong> observational logs, the average ad duration encountered was <strong>`r avg_duration`</strong> seconds, and the longest ad observed lasted for <strong>`r longest_ad`</strong> seconds.
</div>

```{r chart1, fig.align='center'}
# Chart 1: Ads Logged by Platform
latest_data %>%
  ggplot() +
  geom_bar(aes(x = platform, fill = platform)) +
  scale_y_continuous(breaks = function(x) seq(0, max(x), by = 1)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  labs(
    title = "Targeted Ads Logged by Platform",
    x = "Platform",
    y = "Number of Ads",
    caption = "Source: STATS 220 Logging"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.caption = element_text(size = 8, face = "italic", color = "gray50")
  )
```

<br>

```{r chart2, fig.align='center'}
# Chart 2: Average duration per platform
latest_data %>%
  ggplot(aes(x = platform, y = duration_sec, fill = platform)) +
  stat_summary(fun = "mean", geom = "bar") + 
  scale_y_continuous(breaks = function(x) seq(0, max(x), by = 5)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  labs(
    title = "Average Ad Duration by Platform",
    y = "Seconds",
    x = "Platform",
    caption = "Source: STATS 220 Logging"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.caption = element_text(size = 8, face = "italic", color = "gray50")
  )
```
